Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review] {\bf Note that all references to appendices will be replaced with URLs in the final paper; they are appendices only for blind review.}}

### 2022-10-13 paper/Paper.tex
small fixes

The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for Until and Release and the minimum computation lengths for Finally, Global, And, and Or.\\

@@

\subsection{Theoretical Correctness of the WEST Algorithm}
Correctness of the WEST algorithm is dependent on the correctness of subroutines \textit{reg\_prop\_cons}, \textit{reg\_prop\_var}, \textit{join}, \textit{set\_intersect}, \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, and \textit{reg\_R}. 
The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} takes as input a MLTL formula of the appropriate form, and returns the regular expression as previously defined in section \ref{regex}.
\textit{Join} concatenates two input vectors of computation strings $R$ and $T$, which is equivalent to $\mathscr{L}(R) \cup \mathscr{L}(T)$. 
\textit{Set\_intersect} takes as input two vectors of computation strings $R$ and $T$, where $R$ represents $r_1 | ... | r_a$ and $T$ represents $t_1 | ... | t_b$ such that each $r_i$ and $t_j$ are regular expressions over $\Sigma = \{`0', `1', `S', `,'\}$.
Assume that all strings of regular expressions are right padded to equal length. 
We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$. Since a vector of regular expressions is synonymous to the collective Or of each of them, we have that 
\begin{align*}
    \mathscr{L}(R) \cap \mathscr{L}(T) &= \left(\bigcup_{i = 0}^a \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^b \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^a \bigcup_{j = 0}^b \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).
\end{align*}
The for loop in line 3 of \textit{set\_intersect} computes the union of \textit{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.  
Given a computation $\pi$, $\pi \in \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ if and only if $\pi$ matches every character of both $r_i$ and $t_j$. 
$\textit{Bit\_wise\_and}(r_i, t_j)$ compares $r_i$ and $t_j$ character by character and computes their intersection, which is defined naturally: $0 \cap 1 = \emptyset,\ 0 \cap S = 0,\ 1 \cap S = 1, \ 0 \cap 0 = 0, \ 1 \cap 1= 1,\text{ and } S \cap S = S$. 
Note that this operation is commutative. This exhaustively captures all the cases for which $\pi$ must match corresponding characters from $r_i$ and $t_j$. 
Thus $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ and the claim holds.

>>>>

The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for \texttt{Until} and \texttt{Release} and the minimum computation lengths for \texttt{Future}, \texttt{Globally}, \texttt{AND}, and \texttt{OR}.\\

@@

\subsection{Theoretical Correctness of the WEST Algorithm}
Correctness of the WEST algorithm is dependent on the correctness of subroutines \textit{reg\_prop\_cons}, \textit{reg\_prop\_var}, \textit{join}, \textit{set\_intersect}, \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, and \textit{reg\_R}. 
The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} take as input a MLTL formula of the appropriate form, and return the regular expression as %previously
defined in section \ref{regex}.
\textit{Join} concatenates two input vectors of computation strings $R$ and $T$, which is equivalent to $\mathscr{L}(R) \cup \mathscr{L}(T)$. 
\textit{Set\_intersect} takes as input two vectors of computation strings $R$ and $T$, where $R$ represents $r_1 | ... | r_a$ and $T$ represents $t_1 | ... | t_b$ such that each $r_i$ and $t_j$ are regular expressions over $\Sigma = \{`0', `1', `S', `,'\}$.
Assume that all strings of regular expressions are right padded to equal length. 
We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$. Since a vector of regular expressions is synonymous to the collective \texttt{OR} of each of them, we have that 
\begin{align*}
    \mathscr{L}(R) \cap \mathscr{L}(T) &= \left(\bigcup_{i = 0}^a \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^b \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^a \bigcup_{j = 0}^b \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).
\end{align*}
The for loop in line 3 of \textit{set\_intersect} computes the union of \textit{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.  
Given a computation $\pi$, $\pi \in \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ if and only if $\pi$ matches every character of both $r_i$ and $t_j$. 
$\textit{Bit\_wise\_and}(r_i, t_j)$ compares $r_i$ and $t_j$ character by character and computes their intersection, which is defined naturally: $0 \cap 1 = \emptyset,\ 0 \cap S = 0,\ 1 \cap S = 1, \ 0 \cap 0 = 0, \ 1 \cap 1= 1,\text{ and } S \cap S = S$. 
Note that this operation is commutative. This exhaustively captures all the cases for which $\pi$ must match corresponding characters from $r_i$ and $t_j$. 
Thus $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ and the claim holds.
